R Notebook for MSDepression Project

### 2021-02-05 dac_summary.Rmd
Add files via upload

@@

print(paste0("N in EB group w/phq2 = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.2)), " out of ", dim(data_e)[1])) #

print(paste0("N in EB group w/phq9 = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.9)), " out of ", dim(data_e)[1])) #

>>>>

############ Start to synthesie data ###########

@@

print(paste0("N in EB group w/phq2, one time scanners = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.2)), " out of ", dim(data_e)[1])) #

print(paste0("N in EB group w/phq9, one time scanners = ", sum(!is.na(data_e_no_duplicate_EMPI$PHQ.9)), " out of ", dim(data_e)[1])) #

########################
####### overlap ########
########################

eb_icd_and_phq2 <- data_e$ACCESSION_NUM[which(!is.na(data_e[dep_df,]$PHQ.2))] #n = 741
eb_icd_and_phq9 <- data_e$ACCESSION_NUM[which(!is.na(data_e[dep_df,]$PHQ.9))] #n = 106

#overlap of groups
n_melissa <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM))

#unique empis
n_melissa_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM))]))

#overlap of people with just icds
n_melissa_icd <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[dep_df]))
n_melissa_icd_unique_empi <- length(unique(melissa_xls$EMPI[unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[dep_df])]))

#overlap of people with phq2, phq9
n_melissa_phq2 <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.2))]))
n_melissa_phq9 <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.9))]))

#unique people with phq2/9
n_melissa_phq2_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.2))]))]))

n_melissa_phq9_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.9))]))]))

#overlap of icd dx + phq2 or 9
n_melissa_peeps_in_eb_icd_phq2_group <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(eb_icd_and_phq2)) #n = 615
n_melissa_peeps_in_eb_icd_phq9_group <- sum(unique(melissa_xls$ACCESSION_NUM) %in% unique(eb_icd_and_phq9)) #n = 87

#overlap of unique subjects + phq2, phq9 + icd9/10
n_mellisa_peeps_in_eb_icd_phq2_group_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(eb_icd_and_phq2))]))

n_mellisa_peeps_in_eb_icd_phq9_group_unique_empi <- length(unique(melissa_xls$EMPI[(unique(melissa_xls$ACCESSION_NUM) %in% unique(eb_icd_and_phq9))]))
######

print(paste0("n people in Melissa and EB overlap group: ", n_melissa, " out of ", length(unique(data_e$ACCESSION_NUM))))

print(paste0("n people in Melissa and EB overlap group, unique empi: ", n_melissa_unique_empi, " out of ", length(unique(data_e$ACCESSION_NUM))))

print(paste0("n with icd9/10 in Melissa and EB overlap groups: ", n_melissa_icd, " out of ", length(unique(data_e$ACCESSION_NUM[dep_df]))))

print(paste0("n people w/icd9/10 in Melissa and EB overlap group with unique empi: ", n_melissa_icd_unique_empi, " out of ", length(unique(data_e$ACCESSION_NUM))))

print(paste0("n with phq2 in Melissa and EB overlap groups: ", n_melissa_phq2, " out of ", length(unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.2))]))))

print(paste0("n with phq9 in Melissa and EB overlap groups: ", n_melissa_phq9, " out of ", length(unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.9))]))))

print(paste0("n with phq2 in Melissa and EB overlap groups, unique empi: ", n_melissa_phq2_unique_empi, " out of ", length(unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.2))]))))

print(paste0("n with phq9 in Melissa and EB overlap groups, unique empi: ", n_melissa_phq9_unique_empi, " out of ", length(unique(data_e$ACCESSION_NUM[which(!is.na(data_e$PHQ.9))]))))

print(paste0("n with icd and phq2 in Melissa and EB overlap groups: ", n_melissa_peeps_in_eb_icd_phq2_group, " out of ", length(unique(eb_icd_and_phq2))))

print(paste0("n with icd and phq9 in Melissa and EB groups: ", n_melissa_peeps_in_eb_icd_phq9_group, " out of ", length(unique(eb_icd_and_phq9))))

print(paste0("n with icd and phq2 in Melissa and EB overlap groups, unique empi: ", n_mellisa_peeps_in_eb_icd_phq2_group_unique_empi, " out of ", length(unique(eb_icd_and_phq2))))

print(paste0("n with icd and phq9 in Melissa and EB groups, unique empi: ", n_mellisa_peeps_in_eb_icd_phq9_group_unique_empi, " out of ", length(unique(eb_icd_and_phq9))))

###########
#histos
hist(data_e_phq2_unique_empi_combined$PHQ.2, main = paste0("PHQ-2 Histo EB group w/unique EMPI vs all EMPI: n = ", dim(data_e_phq2_unique_empi_combined)[1], "/", length(which(!is.na(data_e$PHQ.2)))), xlab = "PHQ-2", breaks = 6)

### 2021-02-05 lab_notebook.Rmd
Add files via upload

>>>>

#### 20210129

[x] figure out who has unique icd9/10 and phq2/9
[x] figure out what the overlap in # of scans between Melissa and my new group are

#### 20210208
[] check logic of unique EMPIs, looks like something wonky is going on - less unique empis in my group than in the overlap group. Obviously they should be the same if not better
